The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-08-22 razzo-introduction.tex
Do not refer to species pump

We explore such case introducing the multiple-birth death model (MBD), currently absent in BEAST2. The multiple birth hypothesis aims to describe how large-scale environmental changes (also known as species pumps \giovanni{add some ref?}) can lead phylogenies to sport an impressive amount of speciation events in relatively short times.

>>>>

We explore such case introducing the multiple-birth death model (MBD), 
currently absent in BEAST2. 
The multiple birth hypothesis aims to describe how 
large-scale environmental changes can lead phylogenies 
with a high abundance of speciation events in relatively short times.
